Self Regulation Ontology Retest Data Report

### 2018-02-19 code/SRO_Report.Rmd
updating report w new data

get_t_test_out <- function(df){
  out = data.frame(p.value=NA, mean_x = NA, mean_y=NA)
  mod = t.test(df$icc.x, df$icc.y)
  out$p.value = mod$p.value
  out$mean_x = as.numeric(mod$estimate[1])
  out$mean_y = as.numeric(mod$estimate[2])  
  return(out)
}

@@

@@

@@

Plot flat estimates against hierarhical estimates.

Check the distributions of the flat and hierarchical estimates, transform if not normal and t-test to check if they are different than each other (alternatively get difference scores and check if they are different than 0/plot the distribution of the difference scores)

```{r}
retest_hddm_flat <- read.csv(paste0(retest_data_path, 'retest_hddm_flat.csv'))
retest_hddm_flat
```

>>>>

get_t_test_out <- function(df, x = icc.x, y = icc.y){
  out = data.frame(p.value=NA, mean_x = NA, mean_y=NA)
  attach(df)
  mod = t.test(x, y)
  detach(df)
  out$p.value = mod$p.value
  out$mean_x = as.numeric(mod$estimate[1])
  out$mean_y = as.numeric(mod$estimate[2])  
  return(out)
}

@@

[NOT INCLUDED IN DRAFT FOR NOW]

@@

tmp

@@

For retest data plotting hierarchical estimates over flat estimates.

```{r message = FALSE, warning=FALSE}
retest_hddm_flat <- read.csv(paste0(retest_data_path, 'retest_hddm_flat.csv'))
retest_hddm_flat = retest_hddm_flat %>% select(-X) %>% rename(sub_id = subj_id)
retest_hddm_hier = retest_data[,c(names(retest_data) %in% names(retest_hddm_flat))]
retest_hddm_flat = retest_hddm_flat[,c(names(retest_hddm_flat) %in% names(retest_hddm_hier))]

retest_hddm_hier = retest_hddm_hier %>% gather(key, value, -sub_id)
retest_hddm_flat = retest_hddm_flat %>% gather(key, value, -sub_id)

retest_hddm_flat %>%
  left_join(retest_hddm_hier, by=c('sub_id', 'key')) %>%
  ggplot(aes(value.x, value.y, color=key))+
  geom_point()+
  geom_abline(slope=1, intercept=0)+
  theme_bw()+
  theme(legend.position = 'none')+
  xlab('Parameter estimate without hierarchy')+
  ylab('Parameter estimate with hierarchy')
```

For the retest data 6/43 variables have significantly different distributions when they are fit with hierarchy versus without. For all of them the hiearchical estimate distributions have significantly higher means.

```{r message=FALSE, warning=FALSE}
retest_hddm_flat %>%
  left_join(retest_hddm_hier, by=c('sub_id', 'key')) %>%
  group_by(key) %>%
  do(get_t_test_out(.,x=value.x, y=value.y)) %>%
  mutate(flat_diff = ifelse(p.value<0.05, 1, 0)) %>%
  filter(flat_diff == 1) %>%
  mutate(flat_high = ifelse(mean_x>mean_y,1,0))
```

For t1 data plotting hierarchical estimates over flat estimates.

```{r warning=FALSE, message=FALSE}
test_hddm_flat <- read.csv(paste0(retest_data_path, 't1_data/t1_hddm_flat.csv'))
test_hddm_flat = test_hddm_flat %>% select(-X) %>% rename(sub_id = subj_id)
test_hddm_hier = test_data[,c(names(test_data) %in% names(test_hddm_flat))]
test_hddm_flat = test_hddm_flat[,c(names(test_hddm_flat) %in% names(test_hddm_hier))]

test_hddm_hier = test_hddm_hier %>% gather(key, value, -sub_id)
test_hddm_flat = test_hddm_flat %>% gather(key, value, -sub_id)

test_hddm_flat %>%
  left_join(test_hddm_hier, by=c('sub_id', 'key')) %>%
  ggplot(aes(value.x, value.y, color=key))+
  geom_point()+
  geom_abline(slope=1, intercept=0)+
  theme_bw()+
  theme(legend.position = 'none')+
  xlab('Parameter estimate without hierarchy')+
  ylab('Parameter estimate with hierarchy')
```

For the t1 data 3/43 variables have significantly different distributions when they are fit with hierarchy versus without. For all of them the hiearchical estimate distributions have significantly higher means.

```{r message=FALSE, warning=FALSE}
test_hddm_flat %>%
  left_join(test_hddm_hier, by=c('sub_id', 'key')) %>%
  group_by(key) %>%
  do(get_t_test_out(.,x=value.x, y=value.y)) %>%
  mutate(flat_diff = ifelse(p.value<0.05, 1, 0)) %>%
  filter(flat_diff == 1) %>%
  mutate(flat_high = ifelse(mean_x>mean_y,1,0))
```

How does this affect reliability?

```{r}

```
